---
title: "Title of your report"
author: "fmcv76"
date: "02/04/24"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include = FALSE}

knitr::opts_chunk$set(echo = TRUE)

```

## Initial Data Loading and Checks 

```{r include = FALSE}

library(lme4)
library(lmerTest)
library(performance)
library(ggplot2)
library(scales)
library(sjPlot)
library(tidyverse)
library(tinytex)
library(wordcountaddin)

```

```{r}

# Load data 
mst_data_wide = read.csv("https://andygolightly.github.io/teaching/MATH43515/summative/alasdair.csv", 
                    header = TRUE)

# Preprocess long data 
mst_data = mst_data_wide %>% 
  tidyr::pivot_longer(cols = c(Responset1, Responset2, Responset3), 
                      names_to = "Time", 
                      values_to = "Response") %>% # Reshape data to long format 
  dplyr::mutate(Time = case_when(Time == "Responset1" ~ "1", 
                                 Time == "Responset2" ~ "2", 
                                 Time == "Responset3" ~ "3", 
                                 TRUE ~ NA)) %>% 
  dplyr::rename(Treatment = Trt, Nurse = ID) %>% 
  dplyr::mutate(Nurse = as.factor(Nurse), 
                Hospital = as.factor(Hospital), 
                Treatment = as.factor(Treatment), 
                Gender = as.factor(Gender), 
                Size = as.factor(Size), 
                Time = as.factor(Time))

# Preprocess wide data 
mst_data_wide = mst_data_wide %>% 
  dplyr::rename(Treatment = Trt, Nurse = ID) %>% 
  dplyr::mutate(Nurse = as.factor(Nurse), 
                Hospital = as.factor(Hospital), 
                Treatment = as.factor(Treatment), 
                Gender = as.factor(Gender), 
                Size = as.factor(Size))

# Check for NAs
colSums(is.na(mst_data))

```

## Introduction 

__Summary Statistics__

```{r echo = FALSE}

# Summary statistics 
mst_data_wide %>% 
  dplyr::select(-c(Nurse, Hospital)) %>% 
  summary()

```

```{r}

# Distribution of stress scores at month 1 by intervention group histogram 
ggplot(data = mst_data_wide, aes(x = Responset1, fill = Treatment)) +
  geom_histogram(aes(y = after_stat(count)), binwidth = 1, colour = "black", position = "identity", alpha = 0.3) +
  scale_fill_manual(values = c("1" = "red", "0" = "blue"), labels = c("1" = "Treatment Group", "0" = "Control Group"), guide_legend(title = "")) +
  scale_x_continuous(breaks = breaks_width(1), minor_breaks = NULL) +
  scale_y_continuous(breaks = breaks_width(2)) +
  labs(x = "Stress Score", y = "Count", title = "Distribution of Stress Scores Overlaid by Intervention Group - Month 1") +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.5), axis.text = element_text(color = "black", size = 10),
        axis.title = element_text(size = 12), plot.title = element_text(size = 12, face = "bold"))

```

```{r}

# Distribution of stress scores at month 2 by intervention group histogram 
ggplot(data = mst_data_wide, aes(x = Responset2, fill = Treatment)) +
  geom_histogram(aes(y = after_stat(count)), binwidth = 1, colour = "black", position = "identity", alpha = 0.3) +
  scale_fill_manual(values = c("1" = "red", "0" = "blue"), labels = c("1" = "Treatment Group", "0" = "Control Group"), guide_legend(title = "")) +
  scale_x_continuous(breaks = breaks_width(1), minor_breaks = NULL) +
  scale_y_continuous(breaks = breaks_width(2)) +
  labs(x = "Stress Score", y = "Count", title = "Distribution of Stress Scores Overlaid by Intervention Group - Month 2") +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.5), axis.text = element_text(color = "black", size = 10),
        axis.title = element_text(size = 12), plot.title = element_text(size = 12, face = "bold"))

```

```{r}

# Distribution of stress scores at month 3 by intervention group histogram 
ggplot(data = mst_data_wide, aes(x = Responset3, fill = Treatment)) +
  geom_histogram(aes(y = after_stat(count)), binwidth = 1, colour = "black", position = "identity", alpha = 0.3) +
  scale_fill_manual(values = c("1" = "red", "0" = "blue"), labels = c("1" = "Treatment Group", "0" = "Control Group"), guide_legend(title = "")) +
  scale_x_continuous(breaks = breaks_width(1), minor_breaks = NULL) +
  scale_y_continuous(breaks = breaks_width(2)) +
  labs(x = "Stress Score", y = "Count", title = "Distribution of Stress Scores Overlaid by Intervention Group - Month 3") +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.5), axis.text = element_text(color = "black", size = 10),
        axis.title = element_text(size = 12), plot.title = element_text(size = 12, face = "bold"))

```

```{r}

# Distribution of stress scores over time by intervention group histogram 
ggplot(data = mst_data, aes(x = Time, y = Response, colour = Treatment)) +
  stat_boxplot(geom = "errorbar", width = 0.4, coef = 1.5, position = position_dodge(width = 0.75)) +
  geom_boxplot() +
  scale_colour_manual(values = c("1" = "#EC4646", "0" = "#4646EC"), labels = c("1" = "Treatment Group", "0" = "Control Group"), guide_legend(title = "")) +
  scale_y_continuous(breaks = breaks_width(2)) +
  labs(x = "Time (Months Since Treatment)", y = "Stress Score", title = "Distribution of Stress Scores Over Time by Intervention Group - Month 1") +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.5), axis.text = element_text(color = "black", size = 10),
        axis.title = element_text(size = 12), plot.title = element_text(size = 12, face = "bold"))

```

```{r}

# Make time numeric for modelling 
mst_data = mst_data %>% 
  dplyr::mutate(Time = as.numeric(Time))

```

## Analysis 

__3-Level Intercept-Only Model for Time within Nurses within Hospitals__ 

```{r}

# Fit intercept-only model for nurses nested within hospitals 
hospital_nurse_intercept_only_model = lmer(formula = Response ~ 
                                           1 + (1 | Hospital) + 
                                           (1 | Hospital : Nurse), 
                                           data = mst_data)

summary(hospital_nurse_intercept_only_model)

# Calculate ICC 
icc(hospital_nurse_intercept_only_model)

```

__Calculating ICC and VPC Values__

```{r}

# Extract summary of variances 
var_summary = as.data.frame(VarCorr(hospital_nurse_intercept_only_model))

sig = var_summary$vcov[3]  # Residual variance 

sigv = var_summary$vcov[2] # RE variance for school 

sigu = var_summary$vcov[1] # RE variance for class 

totalvar = sum(var_summary$vcov) # Total variance 

vpc_hospital = round(100 * sigv / totalvar, 2)

vpc_nurse = round(100 * sigu / totalvar, 2)

icc_hospital = round(100 * sigv / totalvar, 2)

icc_nurse = round(100 * (sigu + sigv) / totalvar, 2)

```

Overall, there is a `r icc_nurse`% ICC value and therfore `r icc_nurse`% of the variation in Stress Scores can be exlained by the Time nested within Nurses nested within Hospitals grouping structure. There is a `r vpc_nurse`% Response variation (VPC) at the Nurse level and `r vpc_hospital`% VPC at the Hospital level, Therefore `r vpc_nurse`% of the variation in Stress Scores can be explained by the Nurses grouping structure and `r vpc_hospital`% of the variation in Stress Scores can be explained by the Hospitals grouping structure. The high variability between Nurses intuitively makes sense given that measurements pertaining to an individual Nurse should exhibit larger correlation than measurements from different Nurses. Therefore, the Nurse grouping structure should be include in modelling. The `r vpc_hospital`% variability between Hospitals is a relatively large ICC/VPC value in a healthcare setting and therfore the Hopsital grouping structure should be included in modelling. 

```{r}

# Fit random intercept model for time within nurses within hospitals with time level covariate 
random_intercept_Time_model = lmer(formula = Response ~ 
                                   1 + Time + 
                                   (1 | Hospital) + 
                                   (1 | Hospital : Nurse), 
                                   data = mst_data)

summary(random_intercept_Time_model)

```

Time Stamp is statistically significant. 

__Comparison of 3-Level Intercept-Only Model with 3-Level Random Intercept Model with Time Stamp Time Level Covariate__

Test the null hypothesis that the fixed effect of Time Stamp is 0 against an alternative that it is not 0. 

```{r}

anova(hospital_nurse_intercept_only_model, random_intercept_Time_model)

```

- The null hypothesis is rejected and Time Stamp is needed. 

__3-Level Random Intercept Model with Time Stamp Time Level Covariate and Nurse Level Covariates__

```{r}

# Fit random intercept model for time within nurses within hospitals with time level covariate and nurse level covariates 
random_intercept_Time_nurseCovs_model = lmer(formula = Response ~ 
                                             1 + Time + Treatment + Experience + Gender +
                                             (1 | Hospital) + 
                                             (1 | Hospital : Nurse), 
                                             data = mst_data)

summary(random_intercept_Time_nurseCovs_model)

```

Treatment is statistically significant. 
Experience is statistically significant. 
Gender is statistically significant. 

__Comparison of 3-Level Random Intercept Model with Time Stamp Time Level Covariate and 3-Level Random intercept Model with Time Stamp Time Level Covariate and Treatment, Experience, and Gender Nurse Level Covariates__

1. Test the null hypothesis that the fixed effect of Treatment is 0 against an alternative it is not 0. 

2. Test the null hypothesis that the fixed effect of Experience is 0 against an alternative it is not 0. 

3. Test the null hypothesis that the fixed effect of Gender is 0 against an alternative it is not 0. 

```{r}

# Fit random intercept model for time within nurses within hospitals with Time time level covariate and Treatment nurse level covariate 
random_intercept_Time_Treatment_model = lmer(formula = Response ~ 
                                             1 + Time + Treatment + 
                                             (1 | Hospital) + 
                                             (1 | Hospital : Nurse), 
                                             data = mst_data)

# Fit random intercept model for time within nurses within hospitals with Time time level covariate and Treatment and Experience nurse level covariates 
random_intercept_Time_Treatment_Experience_model = lmer(formula = Response ~ 
                                                        1 + Time + Treatment + Experience + 
                                                        (1 | Hospital) + 
                                                        (1 | Hospital : Nurse), 
                                                        data = mst_data)

# Fit random intercept model for time within nurses within hospitals with Time time level covariate and Treatment, Experience, and Gender nurse level covariates 
random_intercept_Time_nurseCovs_model = lmer(formula = Response ~ 
                                             1 + Time + Treatment + Experience + Gender + 
                                             (1 | Hospital) + 
                                             (1 | Hospital : Nurse), 
                                             data = mst_data)

anova(random_intercept_Time_model, random_intercept_Time_Treatment_model, random_intercept_Time_Treatment_Experience_model, random_intercept_Time_nurseCovs_model)

```

1. The null hypothesis is rejected and Treatment is needed. 

2. The null hypothesis is rejected and Experience is needed. 

3. The null hypothesis is rejected and Gender is needed. 

__3-Level Random Intercept Model with Time Stamp Time Level Covariate, Nurse Level Covariates, and Hospital Size Hospital Level Covariate__

```{r}

# Fit random intercept model for time within nurses within hospitals with Time time level covariate, nurse level covariates, and Hospital Size hospital level covariate 
random_intercept_Time_nurseCovs_Size_model = lmer(formula = Response ~ 
                                                  1 + Time + Treatment + Experience + Gender + Size + 
                                                  (1 | Hospital) + 
                                                  (1 | Hospital : Nurse), 
                                                  data = mst_data)

summary(random_intercept_Time_nurseCovs_Size_model)

```

Hospital Size is statistically significant. 

__Comparison of 3-Level Random Intercept Model with Time Stamp Time Level Covariate and Nurse Level Covariates with 3-Level Random Intercept Model with Time Stamp Time Level Covariate, Nurse Level Covariates, and Hospital Size Hospital Level Covariate__

Test the null hypothesis that the fixed effect of Hospital Size is 0 against an alternative that it is not 0. 

```{r}

anova(random_intercept_Time_nurseCovs_model, random_intercept_Time_nurseCovs_Size_model)

```

The null hypothesis is rejected and Hospital Size is needed. 

__3-Level Random Intercept Model with Time Stamp Time Level Covariate (Both Fixed Effect and Random Slope), Nurse Level Covariates, and Hospital Size Hospital Level Covariate__

```{r}

# Fit random intercept model for time within nurses within hospitals with Time time level covariate (Both Fixed Effect and Random Slope), nurse level covariates, and Hospital Size hospital level covariate 
random_intercept_Time_slope_nurseCovs_Size_model = lmer(formula = Response ~ 
                                                        1 + Time + Treatment + Experience + Gender + Size + 
                                                        (1 | Hospital) + 
                                                        (1 + Time | Hospital : Nurse), 
                                                        data = mst_data)

summary(random_intercept_Time_slope_nurseCovs_Size_model)

```

Test the null hypothesis that the random slope for Time is 0 against an alternative that it is not 0. 

```{r}

ranova(random_intercept_Time_slope_nurseCovs_Size_model)

```

The null hypothesis is retained and the random slope for Time is not needed. 

__3-Level Random Intercept Model with Time Stamp Time Level Covariate, Nurse Level Covariates including Experience (Both Fixed Effect and Random Slope), and Hospital Size Hospital Level Covariate__

```{r}

# Fit random intercept model for time within nurses within hospitals with Time time level covariate, nurse level covariates including Experience (Both Fixed Effect and Random Slope), and Hospital Size hospital level covariate 
random_intercept_Time_nurseCovs_Experience_slope_Size_model = lmer(formula = Response ~ 
                                                                   1 + Time + Treatment + Experience + Gender + Size + 
                                                                   (1 | Hospital) + 
                                                                   (1 + Experience | Hospital : Nurse), 
                                                                   data = mst_data)

summary(random_intercept_Time_nurseCovs_Experience_slope_Size_model)

```

Test the null hypothesis that the random slope for Experience is 0 against an alternative that it is not 0. 

```{r}

ranova(random_intercept_Time_nurseCovs_Experience_slope_Size_model)

```

The null hypothesis is retained and the random slope for Experience is not needed. 

__3-Level Random Intercept Model with Time Stamp Time Level Covariate, Nurse Level Covariates, and Hospital Size Hospital Level Covariate with Interaction Between Time and Experience__

```{r}

# Fit random intercept model for time within nurses within hospitals with Time time level covariate, nurse level covariates, and Hospital Size hospital level covariate with interaction between Time and Experience 
random_intercept_Time_nurseCovs_interaction_Size_model = lmer(formula = Response ~ 
                                                              1 + Time * Experience + Treatment + Gender + Size + 
                                                              (1 | Hospital) + 
                                                              (1 | Hospital : Nurse), 
                                                              data = mst_data)

summary(random_intercept_Time_nurseCovs_interaction_Size_model)

```

__Comparison of 3-Level Random Intercept Model with Time Stamp Time Level Covariate, Nurse Level Covariates, and Hospital Size Hospital Level Covariate with 3-Level Random Intercept Model with Time Stamp Time Level Covariate, Nurse Level Covariates, and Hospital Size Hospital Level Covariate with Interaction Between Time and Experience__

Test the null hypothesis that the interaction between Time and Experience is 0 against an alternative that it is not 0. 

```{r}

anova(random_intercept_Time_nurseCovs_Size_model, random_intercept_Time_nurseCovs_interaction_Size_model)

```

The null hypothesis is retained and the interaction between Time and Experience is not needed. 

__Comparison of 3-Level Random Intercept Model with Time Stamp Time Level Covariate, Nurse Level Covariates, and Hospital Size Hospital Level Covariate with 3-Level Random Intercept Model with Time Stamp Time Level Covariate, Nurse Level Covariates, and Hospital Size Hospital Level Covariate with Interaction Between Treatment and Time__

```{r}

# Fit random intercept model for time within nurses within hospitals with Time time level covariate, nurse level covariates, and Hospital Size hospital level covariate with interaction between treatment and time 
final_model = lmer(formula = Response ~ 
                   1 + Treatment + Time + Treatment:Time + Experience + Gender + Size + 
                   (1 | Hospital) + 
                   (1 | Hospital : Nurse), 
                   data = mst_data)

summary(final_model)

```
Test the null hypothesis that the interaction between Treatment and Time is 0 against an alternative that it is not 0. 

```{r}

anova(random_intercept_Time_nurseCovs_Size_model, final_model)

```

The null hypothesis is rejected and the interaction between Treatment and Time is needed. 

## Word Count 

```{r warning = FALSE, include = FALSE}

n_words = paste0("Word Count: ", as.character(word_count()))

```

```{r echo = FALSE}

print(n_words)

```
