---
title: "Assessing the Impact of a Stress Reduction Treatment on Nurses Using a 3-Level (Longitudinal) Multisite Randomised Control Trial"
author: "fmcv76"
date: "02/04/24"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include = FALSE}

knitr::opts_chunk$set(echo = TRUE)

```

```{r include = FALSE}

# Model section titles 
title_1 = "3-Level Intercept-Only Model for Time within Nurses within Hospitals"
title_2 = "3-Level Random Intercept Model with Time Stamp Time Level Covariate"
title_3 = "Comparison of 3-Level Intercept-Only Model with 3-Level Random Intercept Model with Time Stamp Time Level Covariate"
title_4 = "3-Level Random Intercept Model with Time Stamp Time Level Covariate and Nurse Level Covariates"
title_5 = "Comparison of 3-Level Random Intercept Model with Time Stamp Time Level Covariate and 3-Level Random intercept Model with Time Stamp Time Level Covariate and Treatment, Experience, and Gender Nurse Level Covariates"
title_6 = "3-Level Random Intercept Model with Time Stamp Time Level Covariate, Nurse Level Covariates, and Hospital Size Hospital Level Covariate"
title_7 = "Comparison of 3-Level Random Intercept Model with Time Stamp Time Level Covariate and Nurse Level Covariates with 3-Level Random Intercept Model with Time Stamp Time Level Covariate, Nurse Level Covariates, and Hospital Size Hospital Level Covariate"
title_8 = "3-Level Random Intercept Model with Time Stamp Time Level Covariate (Both Fixed Effect and Random Slope), Nurse Level Covariates, and Hospital Size Hospital Level Covariate"
title_9 = "3-Level Random Intercept Model with Time Stamp Time Level Covariate, Nurse Level Covariates, and Hospital Size Hospital Level Covariate with Interaction Between Treatment and Time"
title_10 = "Comparison of 3-Level Random Intercept Model with Time Stamp Time Level Covariate, Nurse Level Covariates, and Hospital Size Hospital Level Covariate with 3-Level Random Intercept Model with Time Stamp Time Level Covariate, Nurse Level Covariates, and Hospital Size Hospital Level Covariate with Interaction Between Treatment and Time"

```

## Initial Data Loading and Checks 

```{r include = FALSE}

library(lme4)
library(lmerTest)
library(performance)
library(ggplot2)
library(scales)
library(sjPlot)
library(tidyverse)
library(tinytex)
library(wordcountaddin)
library(pbkrtest)
library(emmeans)

```

```{r}

# Load data 
filepath = "https://andygolightly.github.io/teaching/MATH43515/summative/alasdair.csv"
mst_data_wide = read.csv(filepath, header = TRUE)

# Preprocess long data 
mst_data = mst_data_wide %>% 
  tidyr::pivot_longer(cols = c(Responset1, Responset2, Responset3), 
                      names_to = "Time", 
                      values_to = "Response") %>% # Reshape data to long format 
  dplyr::mutate(Time = case_when(Time == "Responset1" ~ "1", 
                                 Time == "Responset2" ~ "2", 
                                 Time == "Responset3" ~ "3", 
                                 TRUE ~ NA)) %>% 
  dplyr::rename(Treatment = Trt, Nurse = ID) %>% 
  dplyr::mutate(Nurse = as.factor(Nurse), 
                Hospital = as.factor(Hospital), 
                Treatment = as.factor(Treatment), 
                Gender = as.factor(Gender), 
                Size = as.factor(Size), 
                Time = as.factor(Time))

# Preprocess wide data 
mst_data_wide = mst_data_wide %>% 
  dplyr::rename(Treatment = Trt, Nurse = ID) %>% 
  dplyr::mutate(Nurse = as.factor(Nurse), 
                Hospital = as.factor(Hospital), 
                Treatment = as.factor(Treatment), 
                Gender = as.factor(Gender), 
                Size = as.factor(Size))

# Check for NAs
colSums(is.na(mst_data))

```

## Introduction 

Randomised Control Trials (RCTs) are used to assess the effectiveness of an intervention. Individuals are randomly assigned to either the treatment or control group and this aims to prevent systematic differences between intervention groups with regards to both observables and unobservables, preventing selection into treatment bias. Multisite Randomised Control Trials (MSRCTs) are RCTs which take place across multiple locations with individuals still the unit of randomisation. MSRCTs can allow for a more diverse demographic of individuals studied by including multiple locations, increasing the generalisability of findings. In a healthcare setting this can help ensure that interventions are effective across different demographic groups and geographic locations. However, MSRCTs can be practically and ethically challenging given the intervention randomisation at the individual level. 

This report will assess the results of a 3-level (longitudinal) MSRCT. Nurses from 20 Hospitals were randomly assigned to either the control or treatment group, with the treatment group receiving a stress reduction training intervention. Nurse Stress Scores were collected for 10 Nurses per Hospital, monthly for 3 months post intervention. 

The variables collected as part of the MSRCT were:

- __Time__ - Months post treatment. 
- __Nurse__ - Anonymised Nurse ID. 
- __Hospital__ - Anonymised Hospital ID. 
- __Treatment__ - Flag for whether a Nurse is in the control (0) or treatment (1) group. 
- __Experience__ - Nurse experience in years. 
- __Gender__ - Flag for gender, male (0) or female (1). 
- __Size__ - Flag for whether the A&E department is small (0) or large (1). 
- __Response__ - Stress Score (0-100). 
  
__Research Question:__ Does the stress reduction treatment have a significant impact on Nurse Stress Scores and does this impact vary over Time? 

__Summary Statistics__

```{r echo = FALSE}

# Summary statistics 
mst_data_wide %>% 
  dplyr::select(-c(Nurse, Hospital)) %>% 
  summary()

```

```{r echo = FALSE, fig.height = 4.25}

# Distribution of stress scores at month 1 by intervention group histogram 
ggplot(data = mst_data_wide, aes(x = Responset1, fill = Treatment)) +
  geom_histogram(aes(y = after_stat(count)), binwidth = 1, colour = "black", position = "identity", alpha = 0.3) +
  scale_fill_manual(values = c("1" = "red", "0" = "blue"), labels = c("1" = "Treatment Group", "0" = "Control Group"), guide_legend(title = "")) +
  scale_x_continuous(breaks = breaks_width(1), minor_breaks = NULL) +
  scale_y_continuous(breaks = breaks_width(2)) +
  labs(x = "Stress Score", y = "Count", title = "Distribution of Stress Scores Overlaid by Intervention Group - Month 1") +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.5), axis.text = element_text(color = "black", size = 10),
        axis.title = element_text(size = 12), plot.title = element_text(size = 12, face = "bold"))

```

```{r echo = FALSE, fig.height = 4.25}

# Distribution of stress scores at month 2 by intervention group histogram 
ggplot(data = mst_data_wide, aes(x = Responset2, fill = Treatment)) +
  geom_histogram(aes(y = after_stat(count)), binwidth = 1, colour = "black", position = "identity", alpha = 0.3) +
  scale_fill_manual(values = c("1" = "red", "0" = "blue"), labels = c("1" = "Treatment Group", "0" = "Control Group"), guide_legend(title = "")) +
  scale_x_continuous(breaks = breaks_width(1), minor_breaks = NULL) +
  scale_y_continuous(breaks = breaks_width(2)) +
  labs(x = "Stress Score", y = "Count", title = "Distribution of Stress Scores Overlaid by Intervention Group - Month 2") +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.5), axis.text = element_text(color = "black", size = 10),
        axis.title = element_text(size = 12), plot.title = element_text(size = 12, face = "bold"))

```

```{r echo = FALSE, fig.height = 4.25}

# Distribution of stress scores at month 3 by intervention group histogram 
ggplot(data = mst_data_wide, aes(x = Responset3, fill = Treatment)) +
  geom_histogram(aes(y = after_stat(count)), binwidth = 1, colour = "black", position = "identity", alpha = 0.3) +
  scale_fill_manual(values = c("1" = "red", "0" = "blue"), labels = c("1" = "Treatment Group", "0" = "Control Group"), guide_legend(title = "")) +
  scale_x_continuous(breaks = breaks_width(1), minor_breaks = NULL) +
  scale_y_continuous(breaks = breaks_width(2)) +
  labs(x = "Stress Score", y = "Count", title = "Distribution of Stress Scores Overlaid by Intervention Group - Month 3") +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.5), axis.text = element_text(color = "black", size = 10),
        axis.title = element_text(size = 12), plot.title = element_text(size = 12, face = "bold"))

```

A naive analysis of the above histograms indicates that there is an initial treatment effect and that it reduces over time. The Stress Score distributions of the control and treatment groups start with little overlap, and with each time step the treatment group distribution converges towards the control group distribution i.e. the treatment group Stress Scores increase over time post treatment with the control group remaining similar. 

```{r echo = FALSE}

# Distribution of stress scores over time by intervention group 
ggplot(data = mst_data, aes(x = Time, y = Response, colour = Treatment)) +
  stat_boxplot(geom = "errorbar", width = 0.4, coef = 1.5, position = position_dodge(width = 0.75)) +
  geom_boxplot() +
  scale_colour_manual(values = c("1" = "#EC4646", "0" = "#4646EC"), labels = c("1" = "Treatment Group", "0" = "Control Group"), guide_legend(title = "")) +
  scale_y_continuous(breaks = breaks_width(2)) +
  labs(x = "Time (Months Post Treatment)", y = "Stress Score", title = "Distribution of Stress Scores Over Time by Intervention Group") +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.5), axis.text = element_text(color = "black", size = 10),
        axis.title = element_text(size = 12), plot.title = element_text(size = 12, face = "bold"))

```

A naive analysis of the above plot indicates that the median Stress Score in the treatment group is ~4.5 lower than the control group one month after treatment, with this reducing to ~4 and ~2.5 lower after two and three months respectively. The treatment group Stress Scores increase over time post treatment converging towards the control group at an increase in median Stress Score of ~1 per month. 

```{r echo = FALSE}

# Make time numeric for modelling 
mst_data = mst_data %>% 
  dplyr::mutate(Time = as.numeric(Time))

```

\newpage

## Methods 

Multilevel models help solve the problem when analysing hierarchical data of lower-level-units belonging to the same upper-level-item being correlated. Multilevel models are appropriate for use in this case given the hierarchical structure of the data from the MSRCT. In this context multilevel models can provide more accurate estimates of treatment effects than models which ignore the hierarchical data structure by accounting for the correlation within clusters. The Intraclass Correlation Coefficient (ICC) is a measure of how much variance in the response can be explained by the hierarchical grouping structure of the data. The Variance Partition Coefficient (VPC) is a measure of how much of the variance in the response can be explained by each level in the grouping structure. Both ICC and VPC can be used to assess whether a grouping structure should be included in modelling. 

ICC and VPC values can be calculated as follows:

$$ICC=\frac{\sigma^2_{Hospitals}+\sigma^2_{Nurses}}{\sigma^2_{Hospitals}+\sigma^2_{Nurses}+\sigma^2_{Time}}$$

$$VPC_{Hospitals}=\frac{\sigma^2_{Hospitals}}{\sigma^2_{Hospitals}+\sigma^2_{Nurses}+\sigma^2_{Time}}$$

$$VPC_{Nurses}=\frac{\sigma^2_{Nurses}}{\sigma^2_{Hospitals}+\sigma^2_{Nurses}+\sigma^2_{Time}}$$

Where:

- $\sigma^2_{\text{Time}}$: Variance within Nurses. 
- $\sigma^2_{\text{Nurses}}$: Variance between Nurses within Hospitals. 
- $\sigma^2_{\text{Hospitals}}$: Variance between Hospitals. 


The 3-level structure of the data is as follows: Time nested within Nurses nested within Hospitals. 

- The covariate at the Time level is: Time Stamp. 
- The covariates at the Nurse level are: Treatment, Experience, Gender. 
- The covariate at the Hospital level is: Hospital Size. 

A bottom-up modelling approach will be taken as follows:

- Fit the empty model checking ICC/VPC values for whether to include hierarchical structure. 
- Include lower level covariates and hypothesis test for their inclusion. 
- Include higher level covariates and hypothesis test for their inclusion. 
- Include random slopes and hypothesis test for their inclusion. 
- Include interaction terms and hypothesis test for their inclusion. 

\newpage

## Analysis 

__`r title_1`__ 

```{r}

# Fit intercept-only model for time nested within nurses nested within hospitals 
hospital_nurse_intercept_only_model = lmer(formula = Response ~ 
                                       1 + (1 | Hospital) + 
                                       (1 | Hospital : Nurse), 
                                       data = mst_data)

summary(hospital_nurse_intercept_only_model)

# Calculate ICC 
icc(hospital_nurse_intercept_only_model)

```

__Calculating ICC and VPC Values__

```{r}

# Extract summary of variances 
var_summary = as.data.frame(VarCorr(hospital_nurse_intercept_only_model))

sig = var_summary$vcov[3]  # Residual variance 

sigv = var_summary$vcov[2] # RE variance for Hospital  

sigu = var_summary$vcov[1] # RE variance for Nurse  

totalvar = sum(var_summary$vcov) # Total variance 

vpc_hospital = round(100 * sigv / totalvar, 2)

vpc_nurse = round(100 * sigu / totalvar, 2)

icc = round(100 * (sigu + sigv) / totalvar, 2)

```

The ICC is `r icc`% meaning `r icc`% of the variation in Stress Scores can be explained by the Nurses nested within Hospitals grouping structure. The VPC at the Nurse level is `r vpc_nurse`% and the VPC at the Hospital level is `r vpc_hospital`%, meaning `r vpc_nurse`% of the variation in Stress Scores can be explained by the Nurses grouping structure and `r vpc_hospital`% by the Hospitals grouping structure. The high within Nurse correlation makes sense given that measurements pertaining to an individual Nurse should exhibit larger correlation than measurements from different Nurses. Therefore, the Nurse grouping structure should be include in modelling. The `r vpc_hospital`% variability between Hospitals is a relatively large VPC value in a healthcare setting and therefore the Hospital grouping structure should be included in modelling. 

__`r title_2`__

```{r}

# Fit random intercept model for time within nurses within hospitals 
# with time level covariate 
ri_Time_model = lmer(formula = Response ~ 
                 1 + Time + 
                 (1 | Hospital) + 
                 (1 | Hospital : Nurse), 
                 data = mst_data)

summary(ri_Time_model)

```

Time Stamp is statistically significant. 

__`r title_3`__

Test the null hypothesis that the fixed effect of Time Stamp is 0 against an alternative that it is not 0. 

```{r}

anova(hospital_nurse_intercept_only_model, ri_Time_model)

```

The null hypothesis is rejected and Time Stamp is needed. 

__`r title_4`__

```{r}

# Fit random intercept model for time within nurses within hospitals 
# with time level covariate and nurse level covariates 
ri_Time_nurseCovs_model = lmer(formula = Response ~ 
                           1 + Time + Treatment + Experience + Gender +
                           (1 | Hospital) + 
                           (1 | Hospital : Nurse), 
                           data = mst_data)

summary(ri_Time_nurseCovs_model)

```

Treatment is statistically significant. 

Experience is statistically significant. 

Gender is statistically significant. 

__`r title_5`__

1. Test the null hypothesis that the fixed effect of Treatment is 0 against an alternative it is not 0. 

2. Test the null hypothesis that the fixed effect of Experience is 0 against an alternative it is not 0. 

3. Test the null hypothesis that the fixed effect of Gender is 0 against an alternative it is not 0. 

```{r}

# Fit random intercept model for time within nurses within hospitals 
# with Time time level covariate and Treatment nurse level covariate 
ri_Time_Treatment_model = lmer(formula = Response ~ 
                           1 + Time + Treatment + 
                           (1 | Hospital) + 
                           (1 | Hospital : Nurse), 
                           data = mst_data)

# Fit random intercept model for time within nurses within hospitals 
# with Time time level covariate and Treatment and Experience nurse level covariates 
ri_Time_Treatment_Experience_model = lmer(formula = Response ~ 
                                      1 + Time + Treatment + Experience + 
                                      (1 | Hospital) + 
                                      (1 | Hospital : Nurse), 
                                      data = mst_data)

# Fit random intercept model for time within nurses within 
# hospitals with Time time level covariate and Treatment, 
# Experience, and Gender nurse level covariates 
ri_Time_nurseCovs_model = lmer(formula = Response ~ 
                           1 + Time + Treatment + Experience + Gender + 
                           (1 | Hospital) + 
                           (1 | Hospital : Nurse), 
                           data = mst_data)

anova(ri_Time_model, ri_Time_Treatment_model, 
      ri_Time_Treatment_Experience_model, ri_Time_nurseCovs_model)

```

1. The null hypothesis is rejected and Treatment is needed, and should be included regardless given it is the effect being estimated. 

2. The null hypothesis is rejected and Experience is needed. 

3. The null hypothesis is rejected and Gender is needed. 

\newpage

__`r title_6`__

```{r}

# Fit random intercept model for time within nurses within hospitals 
# with Time time level covariate, nurse level covariates, and Hospital Size 
# hospital level covariate 
ri_Time_nurseCovs_Size_model = lmer(formula = Response ~ 
                                1 + Time + Treatment + Experience + Gender + Size + 
                                (1 | Hospital) + 
                                (1 | Hospital : Nurse), 
                                data = mst_data)

summary(ri_Time_nurseCovs_Size_model)

```

Hospital Size is statistically significant. 

__`r title_7`__

Test the null hypothesis that the fixed effect of Hospital Size is 0 against an alternative that it is not 0. 

```{r}

anova(ri_Time_nurseCovs_model, ri_Time_nurseCovs_Size_model)

```

The null hypothesis is rejected and Hospital Size is needed. 

__`r title_8`__

```{r}

# Fit random intercept model for time within nurses within hospitals 
# with Time time level covariate (Both Fixed Effect and Random Slope), 
# nurse level covariates, and Hospital Size hospital level covariate 
ri_Time_slope_nurseCovs_Size_model = lmer(formula = Response ~ 
                                      1 + Time + Treatment + Experience + Gender + Size + 
                                      (1 | Hospital) + 
                                      (1 + Time | Hospital : Nurse), 
                                      data = mst_data)

summary(ri_Time_slope_nurseCovs_Size_model)

```

Test the null hypothesis that the random slope for Time is 0 against an alternative that it is not 0. 

```{r}

ranova(ri_Time_slope_nurseCovs_Size_model)

```

The null hypothesis is retained and the random slope for Time is not needed. 

__`r title_9`__

```{r}

# Fit random intercept model for time within nurses within hospitals 
# with Time time level covariate, nurse level covariates, and Hospital Size 
# hospital level covariate with interaction between Treatment and Time 
final_model = lmer(formula = Response ~ 
               1 + Treatment + Time + Treatment:Time + Experience + Gender + Size + 
               (1 | Hospital) + 
               (1 | Hospital : Nurse), 
               data = mst_data)

summary(final_model)

```

The interaction between Treatment and Time is statistically significant. 

Time is not statistically significant but should be retained given the statistically significant Treatment Time interaction. 

__`r title_10`__

Test the null hypothesis that the interaction between Treatment and Time is 0 against an alternative that it is not 0. 

```{r}

anova(ri_Time_nurseCovs_Size_model, final_model)

```

The null hypothesis is rejected and the interaction between Treatment and Time is needed. 

\newpage

__Model Diagnostics__

```{r}

plot(final_model)

```

- __Linearity Assumption__ - Points spread roughly evenly above and below the 0 line with some visible lines assessed to be as a result of the discrete nature of Response, therefore the assumption of a linear relationship between predictor variables and the response variable plausibly holds. 
- __Homoscedasticity Assumption__ - There is not an obvious change in spread for the residuals over the range of fitted values, therefore the assumption of residuals having constant variance across different values of the response variable plausibly holds. 

```{r}

residuals_1_to_n_minus_1 = residuals(final_model)[1:(length(residuals(final_model)) - 1)]

residuals_2_to_n = residuals(final_model)[2:length(residuals(final_model))]

plot(residuals_1_to_n_minus_1, residuals_2_to_n)

cor(residuals_1_to_n_minus_1, residuals_2_to_n)

```

There appears to be a small association between adjascent residuals so residuals were randomised and reanalysed. 

```{r}

# Check if randomising rows reduces correlation of adjascent residuals 

set.seed(123)

indices = sample(seq(1, nrow(mst_data), by = 1), replace = FALSE, 
                 prob = rep(1 / nrow(mst_data), nrow(mst_data)))

mst_data_randomised = mst_data[order(indices), ]

# Refit final model with randomised row order 
model_rand = lmer(formula = Response ~ 
                   1 + Treatment + Time + Treatment:Time + Experience + Gender + Size + 
                   (1 | Hospital) + 
                   (1 | Hospital : Nurse), 
                   data = mst_data_randomised)

residuals_1_to_n_minus_1 = residuals(model_rand)[1:(length(residuals(model_rand)) - 1)]

residuals_2_to_n = residuals(model_rand)[2:length(residuals(model_rand))]

plot(residuals_1_to_n_minus_1, residuals_2_to_n)

cor(residuals_1_to_n_minus_1, residuals_2_to_n)

```

- __Independence Assumption__ - The Pearson's correlation between the first 599 residuals (all except the last) and the last 599 residuals (all except the first) is low when the row order of the data is randomised, therefore the assumption of indepentent residuals plausibly holds. 

```{r}

qqnorm(resid(final_model))

qqline(resid(final_model), col = "red") 

```

- __Normality Assumption - Residuals__ - The residuals mostly fit well with the theoretical quantiles of a normal distribution with only a slight deviation at each tail, therefore the assumption of normally distributed residuals plausibly holds. 

```{r}

qqnorm(ranef(final_model)$Hospital[, 1])

qqline(ranef(final_model)$Hospital[, 1], col = "red")

```

- __Normality Assumption - Random Effects - Hospitals__ - The random effects for Hospitals mostly fit well with the theoretical quantiles of a normal distribution with a small deviation at each tail, therefore the assumption of normally distributed random effects plausibly holds. 

```{r}

qqnorm(ranef(final_model)$`Hospital:Nurse`[, 1])

qqline(ranef(final_model)$`Hospital:Nurse`[, 1], col = "red")

```

- __Normality Assumption - Random Effects - Nurses within Hospitals__ - The random effects for Nurses within Hospitals mostly fit well with the theoretical quantiles of a normal distribution with a small deviation at each tail, therefore the assumption of normally distributed random effects plausibly holds. 

__Final Model__

```{r}

summary(final_model)

# Calculate the confidence interval for the average treatment effect at Time 0 
# given the interaction between Treatment and Time 
t0 = emmeans(final_model, specs = ~ Treatment | Time, at = list(Time = 0))

t0_estimates = confint(contrast(t0, method = "trt.vs.ctrl", ref = 1))

t0_mean_treatment_effect = sprintf("%.2f", round(t0_estimates$estimate, 2))
t0_lower_CI = sprintf("%.2f", round(t0_estimates$lower.CL, 2))
t0_upper_CI = sprintf("%.2f", round(t0_estimates$upper.CL, 2))

# Calculate the confidence interval for the average treatment effect at Time 1 
# given the interaction between Treatment and Time 
t1 = emmeans(final_model, specs = ~ Treatment | Time, at = list(Time = 1))

t1_estimates = confint(contrast(t1, method = "trt.vs.ctrl", ref = 1))

t1_mean_treatment_effect = sprintf("%.2f", round(t1_estimates$estimate, 2))
t1_lower_CI = sprintf("%.2f", round(t1_estimates$lower.CL, 2))
t1_upper_CI = sprintf("%.2f", round(t1_estimates$upper.CL, 2))

# Calculate the confidence interval for the average treatment effect at Time 2 
# given the interaction between Treatment and Time 
t2 = emmeans(final_model, specs = ~ Treatment | Time, at = list(Time = 2))

t2_estimates = confint(contrast(t2, method = "trt.vs.ctrl", ref = 1))

t2_mean_treatment_effect = sprintf("%.2f", round(t2_estimates$estimate, 2))
t2_lower_CI = sprintf("%.2f", round(t2_estimates$lower.CL, 2))
t2_upper_CI = sprintf("%.2f", round(t2_estimates$upper.CL, 2))

# Calculate the confidence interval for the average treatment effect at Time 3 
# given the interaction between Treatment and Time 
t3 = emmeans(final_model, specs = ~ Treatment | Time, at = list(Time = 3))

t3_estimates = confint(contrast(t3, method = "trt.vs.ctrl", ref = 1))

t3_mean_treatment_effect = sprintf("%.2f", round(t3_estimates$estimate, 2))
t3_lower_CI = sprintf("%.2f", round(t3_estimates$lower.CL, 2))
t3_upper_CI = sprintf("%.2f", round(t3_estimates$upper.CL, 2))

```

The mean treatment effect is estimated to be -5.41 at Time 0, meaning that Stress Scores are estimated to be on average 5.41 points lower for Nurses who have received the treatment than those who have not, immediately after treatment. Given that the data does not cover Stress Scores at Time 0, this estimate is an extrapolation and should be used with caution. The estimated 95% confidence interval ranges from -6.22 to -4.59 meaning that we are 95% confident that the true effect of the intervention on Stress Scores lies within this range, after controlling for Time, the interaction between Treatment and Time, Experience, Gender, Hospital Size, random effects by Hospital and by Nurses within Hospitals. The treatment effect is statistically significant with a p value of < 0.0001. The below table details the estimated treatment effect at each Time given the interaction between Treatment and Time. 

| Time (Months Post Treatment) | Time 0 | Time 1 | Time 2 | Time 3 | 
|:-------|-------:|-------:|-------:|-------:|
| Average Treatment Effect | `r t0_mean_treatment_effect` | `r t1_mean_treatment_effect` | `r t2_mean_treatment_effect` | `r t3_mean_treatment_effect` |
| Confidence Interval Upper Bound | `r t0_lower_CI` | `r t1_lower_CI` | `r t2_lower_CI` | `r t3_lower_CI` | 
| Confidence Interval Lower Bound | `r t0_upper_CI` | `r t1_upper_CI` | `r t2_upper_CI` | `r t3_upper_CI` | 
| p-value | < 0.0001 | < 0.0001 | < 0.0001 | < 0.0001 | 

The interaction with Time on the mean treatment effect is estimated to be 0.93, meaning that for each unit increase in Time, the mean treatment effect is estimated to decrease by 0.93, i.e. Stress Scores are estimated to increase by 0.93 on average every month which passes post treatment for Nurses in the treatment group. The estimated mean effect of Time on Stress Scores is not statistically significant, with Time included in modelling because of the statistically significant Treatment Time interaction. 

```{r echo = FALSE, fig.height = 4}

# mst_data = mst_data %>% 
#   dplyr::select(-Prediction)

mst_data$Prediction = predict(final_model)

# Subset to only include hospital 9 data 
mst_data_visualisation_subset = mst_data %>% 
  dplyr::filter(Hospital == "9") 

intervention_group_names = c("1" = "Treatment Group", "0" = "Control Group")

ggplot(mst_data_visualisation_subset, aes(Time, Response)) +
  geom_line(aes(y = Prediction, group = Nurse, colour = Nurse)) +
  geom_point(aes(Time, Response, colour = Nurse), size = 1.5, alpha = 0.5, position = position_jitter(width = 0.1, height = 0.25)) +
  geom_smooth(formula = y ~ x, method = "lm", color = "red", se = FALSE, alpha = 0.5) +
  facet_grid(~ Treatment, labeller = as_labeller(intervention_group_names)) +
  scale_x_continuous(breaks = breaks_width(0.5)) +
  scale_y_continuous(breaks = breaks_width(1)) +
  labs(x = "Time (Months Post Treatment)", y = "Stress Score", title = "Final Model - Hospital 9") +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.5), axis.text = element_text(color = "black", size = 10),
        axis.title = element_text(size = 12), plot.title = element_text(size = 12, face = "bold"), legend.position = "none")

```

```{r echo = FALSE, fig.height = 4}

# Subset to only include hospital 16 data 
mst_data_visualisation_subset = mst_data %>% 
  dplyr::filter(Hospital == "16") 

intervention_group_names = c("1" = "Treatment Group", "0" = "Control Group")

ggplot(mst_data_visualisation_subset, aes(Time, Response)) +
  geom_line(aes(y = Prediction, group = Nurse, colour = Nurse)) +
  geom_point(aes(Time, Response, colour = Nurse), size = 1.5, alpha = 0.5, position = position_jitter(width = 0.1, height = 0.25)) +
  geom_smooth(formula = y ~ x, method = "lm", color = "red", se = FALSE, alpha = 0.5) +
  facet_grid(~ Treatment, labeller = as_labeller(intervention_group_names)) +
  scale_x_continuous(breaks = breaks_width(0.5)) +
  scale_y_continuous(breaks = breaks_width(1)) +
  labs(x = "Time (Months Post Treatment)", y = "Stress Score", title = "Final Model - Hospital 16") +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.5), axis.text = element_text(color = "black", size = 10),
        axis.title = element_text(size = 12), plot.title = element_text(size = 12, face = "bold"), legend.position = "none")

```

The above figures visualise the random effects of Nurses within Hospitals 9 and 16, with red lines indicating naive models fit only on the data shown without considering the hierarchical data structure. In the treatment groups Stress Scores are lower and increase with Time in contrast to the control groups. Hospital 9 is small and Hospital 16 is big and the overall increased Stress Scores in big Hospitals can be seen between the two figures. 

## Discussion 

__Research Question__

In regards to the research question: Does the stress reduction treatment have a significant impact on Nurse Stress Scores and does this impact vary over Time?, the estimated mean intervention effect is -5.41 at Time 0, meaning that Stress Scores are estimated to be on average 5.41 points lower for Nurses who have received the treatment than those who have not, immediately after treatment. This effect is statistically significant. Regarding the impact over time, for every month which passes, the mean intervention effect is estimated to decrease by 0.93 points, meaning Stress Scores are estimated to increase by 0.93 on average every month which passes post treatment for Nurses in the treatment group. This effect is statistically significant. Both the impact of the treatment and the impact of the treatment over time can be be seen in the two example figures above and the two tables below. 

| Time (Months Post Treatment) | Time 0 | Time 1 | Time 2 | Time 3 | 
|:-------|-------:|-------:|-------:|-------:|
| Average Treatment Effect | `r t0_mean_treatment_effect` | `r t1_mean_treatment_effect` | `r t2_mean_treatment_effect` | `r t3_mean_treatment_effect` |
| Confidence Interval Upper Bound | `r t0_lower_CI` | `r t1_lower_CI` | `r t2_lower_CI` | `r t3_lower_CI` | 
| Confidence Interval Lower Bound | `r t0_upper_CI` | `r t1_upper_CI` | `r t2_upper_CI` | `r t3_upper_CI` | 
| p-value | < 0.0001 | < 0.0001 | < 0.0001 | < 0.0001 | 

| Group | Time | Mean Stress Score | 
|:-------|--------:|-------:| 
| Control | 1 | 41.2 | 
| Control | 2 | 41.6 | 
| Control | 3 | 41.4 | 
| Treatment | 1 | 36.9 | 
| Treatment | 2 | 38.2 |
| Treatment | 3 | 38.9 | 

The estimated mean treatment effects are relatively large as a proportion of mean Stress Scores initially, however the estimated mean treatment effect reduces quickly over time. A full Cost-Benefit Analysis will need to be undertaken to assess whether the cost of the treatment is worth the short-term Stress Score reduction, given that treatment might need to be repeated frequently to reduce Stress Scores in the long-term. 

__Fixed Effects__

The fixed effect of Experience is estimated to be -0.11, meaning that for every year of Experience a Nurse has, the estimated mean Stress Score decreases by 0.11. 

The fixed effect of Gender is estimated to be 2.09, meaning that the estimated mean Stress Score increases by 2.09 for female Nurses when compared to male Nurses. 

The fixed effect of Hospital Size is estimated to be 1.98, meaning that the estimated mean Stress Score increases by 1.98 for Nurses in large Hospitals when compared to small Hospitals. 

__Limitations__

There are several limitations to the study, including:

- It is questionable whether it is practical or ethical to administer the treatment to individual Nurses in Hospitals but not others. 
- It is not clear how the initial 20 Hospitals were selected from the wider population of Hospitals in the country so there may be selection into experiment bias present. 
- The study is only as reliable as the measurement technique used to capture Nurse Stress Scores, for which the reliability is unknown. 

## Word Count 

```{r warning = FALSE, include = FALSE}

# Minus table words cause they are figures 
n_words = paste0("Word Count: ", as.character(word_count() - 195))

```

```{r echo = FALSE}

print(n_words)

```
