---
title: "Assessing the Impact of a Stress Reduction Treatment on Nurses Using a 3-Level Longitudinal Multisite Randomised Control Trial"
author: "fmcv76"
date: "02/04/24"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include = FALSE}

knitr::opts_chunk$set(echo = TRUE)

```

## Initial Data Loading and Checks 

```{r include = FALSE}

library(lme4)
library(lmerTest)
library(performance)
library(ggplot2)
library(scales)
library(sjPlot)
library(tidyverse)
library(tinytex)
library(wordcountaddin)
library(pbkrtest)
library(emmeans)

```

```{r}

# Load data 
filepath = "https://andygolightly.github.io/teaching/MATH43515/summative/alasdair.csv"

mst_data_wide = read.csv(filepath, header = TRUE)

# Preprocess long data 
mst_data = mst_data_wide %>% 
  tidyr::pivot_longer(cols = c(Responset1, Responset2, Responset3), 
                      names_to = "Time", 
                      values_to = "Response") %>% # Reshape data to long format 
  dplyr::mutate(Time = case_when(Time == "Responset1" ~ "1", 
                                 Time == "Responset2" ~ "2", 
                                 Time == "Responset3" ~ "3", 
                                 TRUE ~ NA)) %>% 
  dplyr::rename(Treatment = Trt, Nurse = ID) %>% 
  dplyr::mutate(Nurse = as.factor(Nurse), 
                Hospital = as.factor(Hospital), 
                Treatment = as.factor(Treatment), 
                Gender = as.factor(Gender), 
                Size = as.factor(Size), 
                Time = as.factor(Time))

# Preprocess wide data 
mst_data_wide = mst_data_wide %>% 
  dplyr::rename(Treatment = Trt, Nurse = ID) %>% 
  dplyr::mutate(Nurse = as.factor(Nurse), 
                Hospital = as.factor(Hospital), 
                Treatment = as.factor(Treatment), 
                Gender = as.factor(Gender), 
                Size = as.factor(Size))

# Check for NAs
colSums(is.na(mst_data))

```

## Introduction 

Randomised Control Trials (RCTs) are used to assess the effectiveness of an intervention. Individuals are randomly assigned to either the treatment or control group and this aims to prevent systematic differences between intervention groups with regards to both observables and unobservables, preventing selection into treatment bias. Multisite Randomised Control Trials (MSRCTs) are RCTs which take place across multiple locations with individual still the unit of randomisation. MSRCTs can allow for a more diverse demographic of individuals studied by including multiple locations, increasing the generalisability of findings. In a healthcare setting this can help ensure that interventions are effective across different demographic groups and geographic locations. 

This report will assess the results of a 3-level longitudinal MSRCT. Nurses from 20 Hospitals were randomly assigned to either the control or treatment group, with the treatment group receiving a stress reduction training intervention. Nurse Stress Scores were collected for 10 Nurses per Hospital, monthly post intervention for 3 months. It is not clear how the initial 20 Hospitals were selected from the wider population of Hospitals in the country so there may be selection into experiment bias present. It appears that all data intended to be collected is present, therefore there does not appear to be selection into observation bias present. 

The variables collected as part of the MSRCT were:

- __Time__ - Months post treatment. 
- __Nurse__ - Anonymised Nurse ID. 
- __Hospital__ - Anonymised Hospital ID. 
- __Treatment__ - Flag for whether a Nurse is in the control (0) or treatment (1) group. 
- __Experience__ - Nurse experience in years. 
- __Gender__ - Flag for gender, male (0) or female (1). 
- __Size__ - Flag for whether the A&E department is small (0) or large (1). 
- __Response__ - Stress Score (0-100). 
  
__Research Question:__ Does the stress reduction treatment have a significant impact on Nurse Stress Scores and does this impact vary over Time? 

__Summary Statistics__

```{r echo = FALSE}

# Summary statistics 
mst_data_wide %>% 
  dplyr::select(-c(Nurse, Hospital)) %>% 
  summary()

```

```{r echo = FALSE}

# Distribution of stress scores at month 1 by intervention group histogram 
ggplot(data = mst_data_wide, aes(x = Responset1, fill = Treatment)) +
  geom_histogram(aes(y = after_stat(count)), binwidth = 1, colour = "black", position = "identity", alpha = 0.3) +
  scale_fill_manual(values = c("1" = "red", "0" = "blue"), labels = c("1" = "Treatment Group", "0" = "Control Group"), guide_legend(title = "")) +
  scale_x_continuous(breaks = breaks_width(1), minor_breaks = NULL) +
  scale_y_continuous(breaks = breaks_width(2)) +
  labs(x = "Stress Score", y = "Count", title = "Distribution of Stress Scores Overlaid by Intervention Group - Month 1") +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.5), axis.text = element_text(color = "black", size = 10),
        axis.title = element_text(size = 12), plot.title = element_text(size = 12, face = "bold"))

```

```{r echo = FALSE}

# Distribution of stress scores at month 2 by intervention group histogram 
ggplot(data = mst_data_wide, aes(x = Responset2, fill = Treatment)) +
  geom_histogram(aes(y = after_stat(count)), binwidth = 1, colour = "black", position = "identity", alpha = 0.3) +
  scale_fill_manual(values = c("1" = "red", "0" = "blue"), labels = c("1" = "Treatment Group", "0" = "Control Group"), guide_legend(title = "")) +
  scale_x_continuous(breaks = breaks_width(1), minor_breaks = NULL) +
  scale_y_continuous(breaks = breaks_width(2)) +
  labs(x = "Stress Score", y = "Count", title = "Distribution of Stress Scores Overlaid by Intervention Group - Month 2") +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.5), axis.text = element_text(color = "black", size = 10),
        axis.title = element_text(size = 12), plot.title = element_text(size = 12, face = "bold"))

```

```{r echo = FALSE}

# Distribution of stress scores at month 3 by intervention group histogram 
ggplot(data = mst_data_wide, aes(x = Responset3, fill = Treatment)) +
  geom_histogram(aes(y = after_stat(count)), binwidth = 1, colour = "black", position = "identity", alpha = 0.3) +
  scale_fill_manual(values = c("1" = "red", "0" = "blue"), labels = c("1" = "Treatment Group", "0" = "Control Group"), guide_legend(title = "")) +
  scale_x_continuous(breaks = breaks_width(1), minor_breaks = NULL) +
  scale_y_continuous(breaks = breaks_width(2)) +
  labs(x = "Stress Score", y = "Count", title = "Distribution of Stress Scores Overlaid by Intervention Group - Month 3") +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.5), axis.text = element_text(color = "black", size = 10),
        axis.title = element_text(size = 12), plot.title = element_text(size = 12, face = "bold"))

```

A naive analysis of the above histograms indicates that there is an initial treatment effect and that it reduces over time. The Stress Score distributions of the control and treatment groups start with little overlap, and with each time step the treatment group distribution converges towards the control group distribution i.e. the treatment group Stress Scores increase over time post treatment with the control group remaining similar. 


```{r echo = FALSE}

# Distribution of stress scores over time by intervention group 
ggplot(data = mst_data, aes(x = Time, y = Response, colour = Treatment)) +
  stat_boxplot(geom = "errorbar", width = 0.4, coef = 1.5, position = position_dodge(width = 0.75)) +
  geom_boxplot() +
  scale_colour_manual(values = c("1" = "#EC4646", "0" = "#4646EC"), labels = c("1" = "Treatment Group", "0" = "Control Group"), guide_legend(title = "")) +
  scale_y_continuous(breaks = breaks_width(2)) +
  labs(x = "Time (Months Post Treatment)", y = "Stress Score", title = "Distribution of Stress Scores Over Time by Intervention Group") +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.5), axis.text = element_text(color = "black", size = 10),
        axis.title = element_text(size = 12), plot.title = element_text(size = 12, face = "bold"))

```

A naive analysis of the above plot indicates that the median Stress Score in the treatment group is ~4.5 lower than the control group one month after treatment, with this reducing to ~4 and ~2.5 lower after two and three months respectively. The treatment group Stress Scores increase over time post treatment converging towards the control group at an increase in median Stress Score of ~1 per month. 

TODO: Add scatter plots and correlations? 

```{r}

# Make time numeric for modelling 
mst_data = mst_data %>% 
  dplyr::mutate(Time = as.numeric(Time))

```

## Methods 

Multilevel models help solve the problem when analysing hierarchical data of lower-level-units belonging to the same upper-level-item being correlated. Multilevel models are appropriate for use in this case given the hierarchical structure of the data from the MSRCT. In this context multilevel models can provide more accurate estimates of treatment effects than models which ignore the hierarchical data structure by accounting for the correlation within clusters. The Intra-class Correlation Coefficient (ICC) is a measure of how much variance in the response can be explained by the hierarchical grouping structure of the data. The Variance Partition Coefficient (VPC) is a measure of how much of the ICC variance can be explained by each level in the grouping structure. Both ICC and VPC can be used to assess whether a grouping structure should be included in modelling. 

The 3-level structure of the data is as follows: Time nested within Nurses nested within Hospitals. 

- The covariate at the Time level is: Time Stamp. 
- The covariates at the Nurse level are: Treatment, Experience, Gender. 
- The covariate at the Hospital level is: Hospital Size. 

A bottom-up modelling approach will be taken as follows:

- Fit the empty model checking ICC/VPC values for whether to include hierarchical structure. 
- Include lower level covariates and hypothesis test for their inclusion. 
- Include higher level covariates and hypothesis test for their inclusion. 
- Include random slopes and hypothesis test for their inclusion. 
- Include interaction terms and hypothesis test for their inclusion. 

## Analysis 

__3-Level Intercept-Only Model for Time within Nurses within Hospitals__ 

```{r}

# Fit intercept-only model for nurses nested within hospitals 
hospital_nurse_intercept_only_model = lmer(formula = Response ~ 
                                       1 + (1 | Hospital) + 
                                       (1 | Hospital : Nurse), 
                                       data = mst_data)

summary(hospital_nurse_intercept_only_model)

# Calculate ICC 
icc(hospital_nurse_intercept_only_model)

```

__Calculating ICC and VPC Values__

```{r}

# Extract summary of variances 
var_summary = as.data.frame(VarCorr(hospital_nurse_intercept_only_model))

sig = var_summary$vcov[3]  # Residual variance 

sigv = var_summary$vcov[2] # RE variance for school 

sigu = var_summary$vcov[1] # RE variance for class 

totalvar = sum(var_summary$vcov) # Total variance 

vpc_hospital = round(100 * sigv / totalvar, 2)

vpc_nurse = round(100 * sigu / totalvar, 2)

icc_hospital = round(100 * sigv / totalvar, 2)

icc_nurse = round(100 * (sigu + sigv) / totalvar, 2)

```

Overall, there is a `r icc_nurse`% ICC value and therefore `r icc_nurse`% of the variation in Stress Scores can be explained by the Time nested within Nurses nested within Hospitals grouping structure. There is a `r vpc_nurse`% Response variation (VPC) at the Nurse level and `r vpc_hospital`% VPC at the Hospital level, Therefore `r vpc_nurse`% of the variation in Stress Scores can be explained by the Nurses grouping structure and `r vpc_hospital`% of the variation in Stress Scores can be explained by the Hospitals grouping structure. The high variability between Nurses intuitively makes sense given that measurements pertaining to an individual Nurse should exhibit larger correlation than measurements from different Nurses. Therefore, the Nurse grouping structure should be include in modelling. The `r vpc_hospital`% variability between Hospitals is a relatively large VPC value in a healthcare setting and therefore the Hopsital grouping structure should be included in modelling. 

__3-Level Random Intercept Model with Time Stamp Time Level Covariate__

```{r}

# Fit random intercept model for time within nurses within hospitals 
# with time level covariate 
ri_Time_model = lmer(formula = Response ~ 
                 1 + Time + 
                 (1 | Hospital) + 
                 (1 | Hospital : Nurse), 
                 data = mst_data)

summary(ri_Time_model)

```

Time Stamp is statistically significant. 

__Comparison of 3-Level Intercept-Only Model with 3-Level Random Intercept Model with Time Stamp Time Level Covariate__

Test the null hypothesis that the fixed effect of Time Stamp is 0 against an alternative that it is not 0. 

```{r}

anova(hospital_nurse_intercept_only_model, ri_Time_model)

```

The null hypothesis is rejected and Time Stamp is needed. 

__3-Level Random Intercept Model with Time Stamp Time Level Covariate and Nurse Level Covariates__

```{r}

# Fit random intercept model for time within nurses within hospitals 
# with time level covariate and nurse level covariates 
ri_Time_nurseCovs_model = lmer(formula = Response ~ 
                           1 + Time + Treatment + Experience + Gender +
                           (1 | Hospital) + 
                           (1 | Hospital : Nurse), 
                           data = mst_data)

summary(ri_Time_nurseCovs_model)

```

Treatment is statistically significant. 

Experience is statistically significant. 

Gender is statistically significant. 

__Comparison of 3-Level Random Intercept Model with Time Stamp Time Level Covariate and 3-Level Random intercept Model with Time Stamp Time Level Covariate and Treatment, Experience, and Gender Nurse Level Covariates__

1. Test the null hypothesis that the fixed effect of Treatment is 0 against an alternative it is not 0. 

2. Test the null hypothesis that the fixed effect of Experience is 0 against an alternative it is not 0. 

3. Test the null hypothesis that the fixed effect of Gender is 0 against an alternative it is not 0. 

```{r}

# Fit random intercept model for time within nurses within hospitals 
# with Time time level covariate and Treatment nurse level covariate 
ri_Time_Treatment_model = lmer(formula = Response ~ 
                           1 + Time + Treatment + 
                           (1 | Hospital) + 
                           (1 | Hospital : Nurse), 
                           data = mst_data)

# Fit random intercept model for time within nurses within hospitals 
# with Time time level covariate and Treatment and Experience nurse level covariates 
ri_Time_Treatment_Experience_model = lmer(formula = Response ~ 
                                      1 + Time + Treatment + Experience + 
                                      (1 | Hospital) + 
                                      (1 | Hospital : Nurse), 
                                      data = mst_data)

# Fit random intercept model for time within nurses within 
# hospitals with Time time level covariate and Treatment, 
# Experience, and Gender nurse level covariates 
ri_Time_nurseCovs_model = lmer(formula = Response ~ 
                           1 + Time + Treatment + Experience + Gender + 
                           (1 | Hospital) + 
                           (1 | Hospital : Nurse), 
                           data = mst_data)

anova(ri_Time_model, ri_Time_Treatment_model, 
      ri_Time_Treatment_Experience_model, ri_Time_nurseCovs_model)

```

1. The null hypothesis is rejected and Treatment is needed, and would be included anyway given it is effect being estimated. 

2. The null hypothesis is rejected and Experience is needed. 

3. The null hypothesis is rejected and Gender is needed. 

__3-Level Random Intercept Model with Time Stamp Time Level Covariate, Nurse Level Covariates, and Hospital Size Hospital Level Covariate__

```{r}

# Fit random intercept model for time within nurses within hospitals 
# with Time time level covariate, nurse level covariates, and Hospital Size 
# hospital level covariate 
ri_Time_nurseCovs_Size_model = lmer(formula = Response ~ 
                                1 + Time + Treatment + Experience + Gender + Size + 
                                (1 | Hospital) + 
                                (1 | Hospital : Nurse), 
                                data = mst_data)

summary(ri_Time_nurseCovs_Size_model)

```

Hospital Size is statistically significant. 

__Comparison of 3-Level Random Intercept Model with Time Stamp Time Level Covariate and Nurse Level Covariates with 3-Level Random Intercept Model with Time Stamp Time Level Covariate, Nurse Level Covariates, and Hospital Size Hospital Level Covariate__

Test the null hypothesis that the fixed effect of Hospital Size is 0 against an alternative that it is not 0. 

```{r}

anova(ri_Time_nurseCovs_model, ri_Time_nurseCovs_Size_model)

```

The null hypothesis is rejected and Hospital Size is needed. 

__3-Level Random Intercept Model with Time Stamp Time Level Covariate (Both Fixed Effect and Random Slope), Nurse Level Covariates, and Hospital Size Hospital Level Covariate__

```{r}

# Fit random intercept model for time within nurses within hospitals 
# with Time time level covariate (Both Fixed Effect and Random Slope), 
# nurse level covariates, and Hospital Size hospital level covariate 
ri_Time_slope_nurseCovs_Size_model = lmer(formula = Response ~ 
                                      1 + Time + Treatment + Experience + Gender + Size + 
                                      (1 | Hospital) + 
                                      (1 + Time | Hospital : Nurse), 
                                      data = mst_data)

summary(ri_Time_slope_nurseCovs_Size_model)

```

Test the null hypothesis that the random slope for Time is 0 against an alternative that it is not 0. 

```{r}

ranova(ri_Time_slope_nurseCovs_Size_model)

```

The null hypothesis is retained and the random slope for Time is not needed. 

TODO: Explain which random slopes were tried? 

TODO: Explain which interactions were tried? 

__Comparison of 3-Level Random Intercept Model with Time Stamp Time Level Covariate, Nurse Level Covariates, and Hospital Size Hospital Level Covariate with 3-Level Random Intercept Model with Time Stamp Time Level Covariate, Nurse Level Covariates, and Hospital Size Hospital Level Covariate with Interaction Between Treatment and Time__

```{r}

# Fit random intercept model for time within nurses within hospitals 
# with Time time level covariate, nurse level covariates, and Hospital Size 
# hospital level covariate with interaction between Treatment and Time 
final_model = lmer(formula = Response ~ 
               1 + Treatment + Time + Treatment:Time + Experience + Gender + Size + 
               (1 | Hospital) + 
               (1 | Hospital : Nurse), 
               data = mst_data)

summary(final_model)

```
Test the null hypothesis that the interaction between Treatment and Time is 0 against an alternative that it is not 0. 

```{r}

anova(ri_Time_nurseCovs_Size_model, final_model)

```

The null hypothesis is rejected and the interaction between Treatment and Time is needed. 

__Model Diagnostics__

```{r}

plot(final_model)

```

- __Linearity Assumption__ - Points spread roughly evenly above and below the 0 line with some visible lines assessed to be as a result of the discrete nature of Response, therefore the assumption of a linear relationship between predictor variables and the response variable plausibly holds. 
- __Homoscedasticity Assumption__ - There is not an obvious change in spread for the residuals over the range of fitted values, therefore the assumption of residuals having constant variance across different values of the response variable plausibly holds. 

```{r}

residuals_1_to_n_minus_1 = residuals(final_model)[1:(length(residuals(final_model)) - 1)]

residuals_2_to_n = residuals(final_model)[2:length(residuals(final_model))]

plot(residuals_1_to_n_minus_1, residuals_2_to_n)

cor(residuals_1_to_n_minus_1, residuals_2_to_n)

```

There appears to be a small association between adjascent residuals so residuals were randomised and reanalysed. 

```{r}

# Check if randomising rows reduces correlation of adjascent residuals 

set.seed(123)

indices = sample(seq(1, nrow(mst_data), by = 1), replace = FALSE, 
                 prob = rep(1 / nrow(mst_data), nrow(mst_data)))

mst_data_randomised = mst_data[order(indices), ]

# Refit final model with randomised row order 
model_rand = lmer(formula = Response ~ 
                   1 + Treatment + Time + Treatment:Time + Experience + Gender + Size + 
                   (1 | Hospital) + 
                   (1 | Hospital : Nurse), 
                   data = mst_data_randomised)

residuals_1_to_n_minus_1 = residuals(model_rand)[1:(length(residuals(model_rand)) - 1)]

residuals_2_to_n = residuals(model_rand)[2:length(residuals(model_rand))]

plot(residuals_1_to_n_minus_1, residuals_2_to_n)

cor(residuals_1_to_n_minus_1, residuals_2_to_n)

```

- __Independence Assumption__ - The Pearson's correlation between the first 599 residuals (all except the last) and the last 599 residuals (all except the first) is low when the row order of the data is randomised, therefore the assumption of indepentent residuals plausibly holds. 

```{r}

qqnorm(resid(final_model))

qqline(resid(final_model), col = "red") 

```

- __Normality Assumption - Residuals__ - The residuals mostly fit well with the theoretical quantiles of a normal distribution with only a slight deviation at each tail, therefore the assumption of normally distributed residuals plausibly holds. 

```{r}

qqnorm(ranef(final_model)$Hospital[, 1])

qqline(ranef(final_model)$Hospital[, 1], col = "red")

```

- __Normality Assumption - Random Effects - Hospitals__ - The random effects for Hospital mostly fit well with the theoretical quantiles of a normal distribution with a small deviation at each tail, therefore the assumption of normally distributed random effects plausibly holds. 

```{r}

qqnorm(ranef(final_model)$`Hospital:Nurse`[, 1])

qqline(ranef(final_model)$`Hospital:Nurse`[, 1], col = "red")

```

- __Normality Assumption - Random Effects - Nurses within Hospitals__ - The random effects for Nurses within Hospitals mostly fit well with the theoretical quantiles of a normal distribution with a small deviation at each tail, therefore the assumption of normally distributed random effects plausibly holds. 

__Final Model__

```{r}

summary(final_model)

# Calculate the confidence interval for the average treatment effect at Time 0 
# given the interaction between Treatment and Time 
t0 = emmeans(final_model, specs = ~ Treatment | Time, at = list(Time = 0))

t0_estimates = confint(contrast(t0, method = "trt.vs.ctrl", ref = 1))

t0_mean_treatment_effect = sprintf("%.2f", round(t0_estimates$estimate, 2))
t0_lower_CI = sprintf("%.2f", round(t0_estimates$lower.CL, 2))
t0_upper_CI = sprintf("%.2f", round(t0_estimates$upper.CL, 2))

# Calculate the confidence interval for the average treatment effect at Time 1 
# given the interaction between Treatment and Time 
t1 = emmeans(final_model, specs = ~ Treatment | Time, at = list(Time = 1))

t1_estimates = confint(contrast(t1, method = "trt.vs.ctrl", ref = 1))

t1_mean_treatment_effect = sprintf("%.2f", round(t1_estimates$estimate, 2))
t1_lower_CI = sprintf("%.2f", round(t1_estimates$lower.CL, 2))
t1_upper_CI = sprintf("%.2f", round(t1_estimates$upper.CL, 2))

# Calculate the confidence interval for the average treatment effect at Time 2 
# given the interaction between Treatment and Time 
t2 = emmeans(final_model, specs = ~ Treatment | Time, at = list(Time = 2))

t2_estimates = confint(contrast(t2, method = "trt.vs.ctrl", ref = 1))

t2_mean_treatment_effect = sprintf("%.2f", round(t2_estimates$estimate, 2))
t2_lower_CI = sprintf("%.2f", round(t2_estimates$lower.CL, 2))
t2_upper_CI = sprintf("%.2f", round(t2_estimates$upper.CL, 2))

# Calculate the confidence interval for the average treatment effect at Time 3 
# given the interaction between Treatment and Time 
t3 = emmeans(final_model, specs = ~ Treatment | Time, at = list(Time = 3))

t3_estimates = confint(contrast(t3, method = "trt.vs.ctrl", ref = 1))

t3_mean_treatment_effect = sprintf("%.2f", round(t3_estimates$estimate, 2))
t3_lower_CI = sprintf("%.2f", round(t3_estimates$lower.CL, 2))
t3_upper_CI = sprintf("%.2f", round(t3_estimates$upper.CL, 2))

```

The mean treatment effect is estimated to be -5.41 at a Time of 0, meaning that Stress Scores are estimated to be on average 5.41 points lower for Nurses who have received the treatment than those who have not, immediately after treatment. Given that the data does not cover Stress Scores at a Time of 0, this estimate is an extrapolation and should be used with caution. The estimated 95% confidence interval ranges from -6.22 to -4.59 meaning that we are 95% confident that the true effect of the intervention on Stress Scores lies within this range, after controlling for Time, the interaction between Treatment and Time, Experience, Gender, Hospital Size, random effects by Hospital and by Nurses within Hospitals. The treatment effect is statistically significant with a p value of < 0.0001. The below table details the estimated treatment effect at each Time value given the interaction between Treatment and Time. 

| Time (Months Post Treatment) | Time 0 | Time 1 | Time 2 | Time 3 | 
|-------|-------|-------|-------|-------|
| Average Treatment Effect | `r t0_mean_treatment_effect` | `r t1_mean_treatment_effect` | `r t2_mean_treatment_effect` | `r t3_mean_treatment_effect` |
| Confidence Interval Upper Bound | `r t0_lower_CI` | `r t1_lower_CI` | `r t2_lower_CI` | `r t3_lower_CI` | 
| Confidence Interval Lower Bound | `r t0_upper_CI` | `r t1_upper_CI` | `r t2_upper_CI` | `r t3_upper_CI` | 
| p-value | < 0.0001 | < 0.0001 | < 0.0001 | < 0.0001 | 

The interaction with Time on the mean treatment effect is estimated to be 0.93, meaning that for each unit increase in Time, the mean treatment effect is estimated to decrease by 0.93, i.e. the mean treatment effect is estimated to decrease by 0.93 and therefore Stress Scores are estimated to increase by 0.93 on average every month which passes post Treatment for Nurses in the treatment group. The estimated mean effect of Time on Stress Scores is not statistically significant, with Time included in modelling because of the statistically significant interaction between Treatment and Time. 

The fixed effect of Experience is estimated to be -0.11, meaning that for every year of Experience a Nurse has, the estimated mean Stress Score decreases by 0.11. 

The fixed effect of Gender is estimated to be 2.09, meaning that the estimated mean Stress Score increases by 2.09 for female Nurses when compared to male Nurses. 

The fixed effect of Hospital Size is estimated to be 1.98, meaning that the estimated mean Stress Score increases by 1.98 for Nurses in large Hospitals when compared to small Hospitals. 

TODO: Work out how to calculate confidence intervals given Treatment Time interaction 

```{r echo = FALSE}

# mst_data = mst_data %>% 
#   dplyr::select(-Prediction)

mst_data$Prediction = predict(final_model)

# Subset to only include hospital 9 data 
mst_data_visualisation_subset = mst_data %>% 
  dplyr::filter(Hospital == "9") 

intervention_group_names = c("1" = "Treatment Group", "0" = "Control Group")

ggplot(mst_data_visualisation_subset, aes(Time, Response)) +
  geom_line(aes(y = Prediction, group = Nurse, colour = Nurse)) +
  geom_point(aes(Time, Response, colour = Nurse), size = 1.5, alpha = 0.5, position = position_jitter(width = 0.1, height = 0.25)) +
  geom_smooth(formula = y ~ x, method = "lm", color = "red", se = FALSE, alpha = 0.5) +
  facet_grid(~ Treatment, labeller = as_labeller(intervention_group_names)) +
  scale_x_continuous(breaks = breaks_width(0.5)) +
  scale_y_continuous(breaks = breaks_width(1)) +
  labs(x = "Time (Months Post Treatment)", y = "Stress Score", title = "Final Model - Hospital 9") +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.5), axis.text = element_text(color = "black", size = 10),
        axis.title = element_text(size = 12), plot.title = element_text(size = 12, face = "bold"), legend.position = "none")

```

Example of small hospital. 

```{r echo = FALSE}

# Subset to only include hospital 16 data 
mst_data_visualisation_subset = mst_data %>% 
  dplyr::filter(Hospital == "16") 

intervention_group_names = c("1" = "Treatment Group", "0" = "Control Group")

ggplot(mst_data_visualisation_subset, aes(Time, Response)) +
  geom_line(aes(y = Prediction, group = Nurse, colour = Nurse)) +
  geom_point(aes(Time, Response, colour = Nurse), size = 1.5, alpha = 0.5, position = position_jitter(width = 0.1, height = 0.25)) +
  geom_smooth(formula = y ~ x, method = "lm", color = "red", se = FALSE, alpha = 0.5) +
  facet_grid(~ Treatment, labeller = as_labeller(intervention_group_names)) +
  scale_x_continuous(breaks = breaks_width(0.5)) +
  scale_y_continuous(breaks = breaks_width(1)) +
  labs(x = "Time (Months Post Treatment)", y = "Stress Score", title = "Final Model - Hospital 16") +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.5), axis.text = element_text(color = "black", size = 10),
        axis.title = element_text(size = 12), plot.title = element_text(size = 12, face = "bold"), legend.position = "none")

```

Example of big hospital. 

## Word Count 

```{r warning = FALSE, include = FALSE}

n_words = paste0("Word Count: ", as.character(word_count()))

```

```{r echo = FALSE}

print(n_words)

```
